Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2018-03-13 paper/reply_reviews/reply_comments.tex
New changes in revision and added q_init and x_target for comparison

\item \textit{`some details about the optimization problem in (8) might be given
(nature of the problem, complexity, feasibility)."}\\
\textcolor{red}{\texttt{Response:} \small TODO..}\\

>>>>

\item \textit{`some details about the optimization problem in (8) might be given
(nature of the problem, complexity, feasibility)."}\\
\textcolor{red}{\texttt{Response:} \small The following has been added near Eq. (8):\\
``The resulting optimization minimizes the mean squared joint velocity error from \eqref{eq:optim_error}, resulting in a convex semidefinite optimization with a quadratic objective..."
``This optimization is always feasible (the only constraint is that the $A_k$s be independently PSD), and the number of terms in the objective is $O\left(k^2d^3\left( \sum_{n=1}^N T_n\right)\right)$."\\
To elaborate about the prior calculation: the number of terms in the sum is proportional to the number of recorded points, times the number of matrices (k) required to generate the predicted velocity from (7) squared, times the number of terms in a matrix multiplication of two $d x d$ matrices ($d^3$).}\\

### 2018-03-13 paper/submitted-v2-revised/main_RA-L_v2_revised.tex
New changes in revision and added q_init and x_target for comparison

Intuitively, each ``synergy region" in synergy space is defined by a Gaussian distribution, and the closer the robot is to a region, the more that region's synergy ($A_k$) influences the robot's current joint-space motions. Finding the appropriate synergy matrices $A_k$ to accurately reproduce the observed behaviors can be reduced to a convex semidefinite optimization, with the goal of minimizing \eqref{eq:optim_error}. To achieve this, the following optimization is proposed which uses mean square error as a means to minimize the joint velocity error from \eqref{eq:optim_error} as follows:
\begin{equation}
\vspace{-10pt}
\begin{aligned}
&\underset{A_1, \dots, A_K}{\text{min}} 
\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d;t,n} - f(q_{t,n}) \right \| \\
& \text{subject to}&\\
&  0 \prec A_k, \; \forall k \in \{1, \dots, K\}. &
\end{aligned}
\label{eq:opt}
\end{equation}
where $f(q_{t,n})$ is calculated by %combining our dynamical system formulation
 \eqref{eq:ds} with \eqref{eq:A}, and $x^*_{n}$ is defined as the endpoint of the $ n^{\text{th}} $ demonstrated trajectory.

>>>>

Intuitively, each ``synergy region" in synergy space is defined by a Gaussian distribution, and the closer the robot is to a region, the more that region's synergy ($A_k$) influences the robot's current joint-space motions. Finding the appropriate synergy matrices $A_k$ to accurately reproduce the observed behaviors can be reduced to a semidefinite program with the goal of minimizing \eqref{eq:optim_error}. The resulting optimization minimizes the mean squared joint velocity error from \eqref{eq:optim_error}, resulting in a convex semidefinite optimization with a quadratic objective, as follows:
\begin{equation}
\vspace{-10pt}
\begin{aligned}
&\underset{A_1, \dots, A_K}{\text{min}} 
\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d;t,n} - f(q_{t,n}) \right \| \\
& \text{subject to}&\\
&  0 \prec A_k, \; \forall k \in \{1, \dots, K\}. &
\end{aligned}
\label{eq:opt}
\end{equation}
where $f(q_{t,n})$ is calculated by %combining our dynamical system formulation
 \eqref{eq:ds} with \eqref{eq:A}, and $x^*_{n}$ is defined as the endpoint of the $ n^{\text{th}} $ demonstrated trajectory. This optimization is always feasible (the only constraint is that the $A_k$s be independently PSD), and the number of terms in the objective is roughly $O\left(k^2d^3\left( \sum_{n=1}^N T_n\right)\right)$.
